Canonical rings of $\bq$-divisors on Minimal Rational Surfaces

### 2015-08-09 surfaces-write-up/surface-write-up.tex
intro M_g explanation todo

Another closely related topic is the Hassett-Keel program 
initiated in \cite{hassett:classical-and-minimal-models}, which aims to describe log canonical models of the form
\begin{align*}
	\overline {\mathscr M}_g(\alpha) := \bigoplus_{d \geq 0} u^d H^0 \left(
	\overline {\mathscr M}_g, \lfloor d K_{\overline{\mathscr M}_g} +
	\alpha\delta \rfloor  \right) 
\end{align*}
in terms of certain moduli spaces. Moreover, $\bq$-divisors on surfaces also naturally
appear when considering the canonical ring of surfaces of Kodaira dimension 1.
A surface has Kodaira dimension 1 if and only if it is an elliptic surface \cite[p. 244]{
barthHPV:compactComplexSurfaces}, and
the canonical rings of elliptic surfaces most naturally described in the setting of
$\bq$-divisors \cite[Chapter V, Theorem 12.1]{barthHPV:compactComplexSurfaces}.

>>>>

Another closely related topic is the Hassett-Keel program 
initiated in \cite{hassett:classical-and-minimal-models}, which aims to describe log canonical models of the form \todo{Robin: define $\mathscr{M}_g$? Not sure what this is.}
\begin{align*}
	\overline {\mathscr M}_g(\alpha) := \bigoplus_{d \geq 0} u^d H^0 \left(
	\overline {\mathscr M}_g, \lfloor d K_{\overline{\mathscr M}_g} +
	\alpha\delta \rfloor  \right) 
\end{align*}
in terms of certain moduli spaces. Moreover, $\bq$-divisors on surfaces also naturally
appear when considering the canonical ring of surfaces of Kodaira dimension 1.
A surface has Kodaira dimension 1 if and only if it is an elliptic surface \cite[p. 244]{
barthHPV:compactComplexSurfaces}, and
the canonical rings of elliptic surfaces most naturally described in the setting of
$\bq$-divisors \cite[Chapter V, Theorem 12.1]{barthHPV:compactComplexSurfaces}.
